---
title: "Three Class Model - Multinomial Logistic Reg"
author: "Junhua Yang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    fig_height: 4.5
    fig_width: 6.5
    highlight: monochrome
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = "  ", prompt=TRUE, warning = FALSE, 
                      echo=FALSE, message = FALSE, include=FALSE, eval.expr = TRUE)
options(max.print=5000)
```

# load data
```{r}
library(dplyr)
library(magrittr)
library(ggplot2)
library(tableone)
library(car)
library(knitr)
library(MASS)
library(reshape2)
library(rsq)
library(nnet)
library(gridExtra)
library(generalhoslem)


df = read.csv("C:/Users/1130j/Desktop/Yale/Data/all_recent_tweets_text_score_8_parsed.csv")

dim(df) #1197

```

# Class Distribution
```{r, include=TRUE, echo=TRUE}
table(df$classname) %>% addmargins() #very few awareness

# str(df)

df2 = subset(df, df$classname != 'awareness')
df2 %>% dim

df2$classname = factor(df2$classname)
df2$class <- factor(df2$class)


df2$threeclass = NA
df2$threeclass[df2$classname == 'None'] = 0
df2$threeclass[df2$classname == 'pain'] = 1
df2$threeclass[df2$classname %in%  c('pleasure', 'addiction')] = 2


table(df2$threeclass, df2$classname) %>% addmargins()

```

```{r}
make.frm <- function(vars){
  frm <- paste("threeclass ~ ", paste(vars, collapse=" + ")) %>% as.formula
  return(frm)
}

```


# Define Features
```{r}
vars <- c('imaginative', 'netspeak_focus', 'persuasive', 'liberal', 'self_assured', 'body_focus',
       'trusting', 'organized', 'type_a', 'intellectual', 'cheerful',
       'disciplined', 'neuroticism', 'cooperative', 'social_skills',
       'openness', 'aggressive', 'adjustment', 'religion_oriented',
       'empathetic', 'food_focus', 'generous', 'sexual_focus',
       'thinking_style', 'friend_focus', 'extraversion', 'agreeableness',
       'depression', 'ambitious', 'friendly', 'money_oriented', 'independent',
       'melancholy', 'workhorse', 'reward_bias', 'energetic', 'happiness',
       'self_conscious', 'assertive', 'insecure', 'leisure_oriented',
       'impulsive', 'cautious', 'conscientiousness', 'active', 'power_driven',
       'dutiful', 'genuine', 'adventurous', 'sociable', 'family_oriented',
       'cold', 'emotionally_aware', 'humble', 'anxious', 'artistic',
       'stressed', 'health_oriented', 'work_oriented')

set.seed(1234)
frm0 = make.frm(vars)
mod0 = multinom(frm0, data=df2)
mod0 %>% Anova()
```

# Backward selection using BIC
```{r}
BIC_Result = stepAIC(mod0, direction="backward", k=log(nrow(df2))) #k = log(n) refers to BIC

```

```{r, include=TRUE}
BIC_Result

BIC_Result$anova
```


# Backward selection using AIC
```{r}
AIC_Result = stepAIC(mod0, direction="backward", trace=TRUE) 
```

```{r, include=TRUE}
AIC_Result

AIC_Result$anova

```



```{r}
modBIC = multinom(threeclass ~ netspeak_focus + money_oriented + 
       workhorse + active + power_driven + health_oriented, data=df2)
modBIC %>% summary


modBIC %>% Anova()
```

```{r}
modAIC = multinom(threeclass ~ netspeak_focus + liberal + self_assured + cheerful + 
    cooperative + aggressive + religion_oriented + sexual_focus + 
    friend_focus + depression + ambitious + melancholy + workhorse + 
    self_conscious + leisure_oriented + active + power_driven + 
    genuine + cold + anxious + health_oriented + work_oriented, data=df2)

modAIC %>% summary


modAIC %>% Anova()
```




# BIC 20 Coefficients
```{r, include=TRUE, echo=TRUE}
modBIC20= multinom(threeclass ~ netspeak_focus + money_oriented + workhorse + active + power_driven + 
                     health_oriented + adjustment + reward_bias + cheerful + leisure_oriented + 
                     thinking_style + aggressive + organized + self_assured + religion_oriented + 
                     cautious + impulsive + disciplined + type_a + liberal, data=df2)

modBIC20 %>% summary
modBIC20 %>% Anova()

```


# BIC 25 Coefficients
```{r, include=TRUE, echo=TRUE}
modBIC25= multinom(threeclass ~ netspeak_focus + money_oriented + workhorse + active + power_driven + 
                     health_oriented + adjustment + reward_bias + cheerful + leisure_oriented + 
                     thinking_style + aggressive + organized + self_assured + religion_oriented + 
                     cautious + impulsive + disciplined + type_a + liberal + 
                     melancholy + neuroticism + sexual_focus + food_focus + cold, data=df2)

modBIC25 %>% summary
modBIC25 %>% Anova()

```

# BIC 30 Coefficients
```{r, include=TRUE, echo=TRUE}
modBIC30= multinom(threeclass ~ netspeak_focus + money_oriented + workhorse + active + power_driven + 
                     health_oriented + adjustment + reward_bias + cheerful + leisure_oriented + 
                     thinking_style + aggressive + organized + self_assured + religion_oriented + 
                     cautious + impulsive + disciplined + type_a + liberal + 
                     melancholy + neuroticism + sexual_focus + food_focus + cold + 
                     friend_focus + agreeableness + generous + genuine + self_conscious, data=df2)

modBIC30 %>% summary
modBIC30 %>% Anova()

```

# BIC 40 Coefficients
```{r, include=TRUE, echo=TRUE}
modBIC40= multinom(threeclass ~ netspeak_focus + money_oriented + workhorse + active + power_driven +
                     health_oriented + adjustment + reward_bias + cheerful + leisure_oriented + 
                     thinking_style + aggressive + organized + self_assured + religion_oriented +
                     cautious + impulsive + disciplined + type_a + liberal + 
                     melancholy + neuroticism + sexual_focus + food_focus + cold +
                     friend_focus + agreeableness + generous  + genuine + self_conscious +
                     emotionally_aware + artistic + ambitious + adventurous + anxious +
                     stressed + work_oriented + depression + family_oriented + insecure, data=df2)

modBIC40 %>% summary
modBIC40 %>% Anova()

```


### Report```````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````````
```{r, include=TRUE, echo=TRUE}
modBIC40= multinom(threeclass ~ netspeak_focus + money_oriented + workhorse + active + power_driven +
                     health_oriented + adjustment + reward_bias + cheerful + leisure_oriented + 
                     thinking_style + aggressive + organized + self_assured + religion_oriented +
                     cautious + impulsive + disciplined + type_a + liberal + 
                     melancholy + neuroticism + sexual_focus + food_focus + cold +
                     friend_focus + agreeableness + generous  + genuine + self_conscious +
                     emotionally_aware + artistic + ambitious + adventurous + anxious +
                     stressed + work_oriented + depression + family_oriented + insecure, data=df2)

modBIC40 %>% summary
modBIC40 %>% Anova()

```


# Goodness of fit test for the overall model
```{r, include=TRUE}
hoslem.result.BIC <- logitgof(df2$threeclass, fitted(modBIC, outcome=FALSE), ord=FALSE) 
hoslem.result.BIC 

hoslem.result.AIC <- logitgof(df2$threeclass, fitted(modAIC, outcome=FALSE), ord=FALSE) 
hoslem.result.AIC 

hoslem.result.AIC2 <- logitgof(df2$threeclass, fitted(modAIC, outcome=FALSE), ord=FALSE) 
hoslem.result.AIC2 
```



